---
toc: true
toc-depth: 3
title: "Mixed model analysis - summary Bright and Dark (REALL ILLUMINANT)"
format: html
editor: visual
---

Open .RData file "data.RData"

```{r}
load(../data.RData)

```

# Mixed models analysis

```{r}
#| echo: false
#| output: false

#load libraries
library(emmeans)
library(scales)
library(stargazer)
library(pavo)
library(readr)
library(dplyr)
library(lme4)
library(nlme)
library(lmerTest)
library(afex)
library(multcomp)
library(mapproj)
library(ggplot2)
library(patchwork)
library(modelsummary)
```

#### Load dark luminant:

```{r}
#Locate your folder with single file containing mean dark illuminant spectrum - "dark_lum.csv"
setwd("../dark illuminant/")

dark.luminant <- getspec(
  ext = "csv",
  lim = c(300, 700),
  decimal = ".",
  sep = "space",
  subdir = FALSE,
  subdir.names = FALSE,
  ignore.case = TRUE)

#smoothing dark.luminant
dark.luminant<- procspec(fixneg = "zero", dark.luminant, opt = "smooth", span = 0.05)
dark.lum <- dark.luminant

dark.luminant <- procspec(dark.luminant, fixneg = 'zero')
plot(dark.luminant, type = "overlay")


```

#### Load bright luminant:

```{r}
#Locate your folder with single file containing mean bright illuminant spectrum - "bright_lum.csv"
setwd("../bright illuminant")

bright.luminant <- getspec(
  ext = "csv",
  lim = c(300, 700),
  decimal = ".",
  sep = "space",
  subdir = FALSE,
  subdir.names = FALSE,
  ignore.case = TRUE)

#smoothing bright.luminant
bright.luminant <- procspec(fixneg = "zero", bright.luminant, opt = "smooth", span = 0.05)
bright.lum <- bright.luminant

plot(bright.luminant, type = "overlay")


```

#### Create plot with two luminants

```{r}
luminant <- left_join(dark.luminant, bright.luminant, by = "wl")

luminant <- luminant %>%
  rename(bright_lum = "bright lum")


irr <- ggplot() +
  geom_line(data = luminant, aes(x = wl, y = dark_lum), lwd = 1, color = "coral1") +
  geom_line(data = luminant, aes(x = wl, y = bright_lum), lwd = 1, color = "turquoise2") +
  ylab('Irradiance (µMol/s/mr2/nm)') + xlab('Wavelength (nm)') +
  theme_bw() + theme(text = element_text(size = 14))
  

irr

```

(In this document I have omitted the analysis of distances. It is unnecessary here but if so, remember to use bootcol.distances with Blue tit single cone ratio is **1, 1.92, 2.68, 2,70)**

# DB

## Visual models

### Visual model for bright nest boxes

```{r}
is.rspec(bright.specs)
vm_bright <- vismodel(bright.specs, visual = "avg.uv", illum = bright.luminant, qcatch="Qi", relative=T, achromatic = "bt.dc", trans = "bluetit", vonkries = F)
```

### Visual model for dark nest boxes

```{r}
is.rspec(dark.specs) 
vm_dark <- vismodel(dark.specs, visual = "avg.uv", illum = dark.luminant, qcatch="Qi", relative=F, achromatic = "bt.dc", trans = "bluetit", vonkries = F) 
```

### TCS DB - Dark and Bright illuminant

```{r}
vm_DB <- bind_rows(vm_dark, vm_bright)

TCS_DB <-colspace(vm_bright,
              space = c("tcs"))
```

*Write TCS_DB as a .csv and add data with spectral variables S9, S1U, H4 etc. from spec_var.csv database, all saved as a TCS_DB_data.csv*

```{r}

#add new variable TypeAge
TCS_DB_data <- TCS_DB_data %>%
  mutate(TypeAge = paste0(Type, Age))
#scale S9
TCS_DB_data <- TCS_DB_data %>%

  mutate(h.theta_s = scale(h.theta),
         h.phi_s = scale(h.phi),
         r.achieved_s = scale(r.achieved),
         B1_s = scale(B1), 
         H4_s = scale(H4),
         S9_s = scale(S9), 
         S5_s = scale(S5),
         lum_s = scale(lum))


```

mr - (m)odel includes (r)eal illumiant - bright and dark illuminant (depending on experimental group)

Dependent variables in models:

mr1 - h.theta_s\
mr2 - h.phi_s\
mr3 - r.achieved_s\
mr4 - lum_S\
mr5 - S9_s\

```{r}
TCS_DB_data$Individual <- as.factor(TCS_DB_data$Individual)
TCS_DB_data$Type <- as.factor(TCS_DB_data$Type)
TCS_DB_data$Nestbox <- as.factor(TCS_DB_data$Nestbox)
TCS_DB_data$Age <- as.factor(TCS_DB_data$Age)
TCS_DB_data$Region <- as.factor(TCS_DB_data$Region)
TCS_DB_data$TypeAge <- as.factor(TCS_DB_data$TypeAge)
```

```{r}
TCS_DB_data.side <- subset(TCS_DB_data, Region == "Side")
TCS_DB_data.maxi <- subset(TCS_DB_data, Region == "Maxilla")
TCS_DB_data.mand <- subset(TCS_DB_data, Region == "Mandible")
TCS_DB_data.pala <- subset(TCS_DB_data, Region == "Palate")
```

# mr1 - h.theta

```{r}
#| echo: false
#| output: false

TCS_DB_data.maxi$Type <- relevel(TCS_DB_data.maxi$Type, ref = "Dark")
TCS_DB_data.pala$Type <- relevel(TCS_DB_data.pala$Type, ref = "Dark")
TCS_DB_data.side$Type <- relevel(TCS_DB_data.side$Type, ref = "Dark")
TCS_DB_data.mand$Type <- relevel(TCS_DB_data.mand$Type, ref = "Dark")

mr1.side <- lmer(h.theta_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.side)
mr1.maxi <- lmer(h.theta_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.maxi)
mr1.mand <- lmer(h.theta_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.mand)
mr1.pala <- lmer(h.theta_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.pala)
summary(mr1.)
class(mr1.side) <- "lmerMod"
class(mr1.maxi) <- "lmerMod"
class(mr1.mand) <- "lmerMod" 
class(mr1.pala) <- "lmerMod"
```

```{r}
#| echo: false
h.theta_s.sum <- stargazer(mr1.side, mr1.mand, mr1.maxi, mr1.pala, digits = 2, type = "text", style = "default", title = "h.theta_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))
```

## Side

```{r}
summary(mr1.side)

rmr1.side.TypeAge <-lmer(h.theta_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.side)
mr1.side.EM <- emmeans(mr1.side.TypeAge, ~TypeAge)

plot.mr1.side <- plot(mr1.side.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.theta_s Side", plotit = F)

head(plot.mr1.side)
plot.mr1.side$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr1.side$group <- c("BF", "DF", "DF" ,"BF")
plot.mr1.side$group1 <- c("A1", "A2", "A1" ,"A2")


rsidetheta <- ggplot(plot.mr1.side, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  ggtitle("Flanges") + 
  geom_hline(yintercept = plot.mr1.side[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") + 
  geom_point(size = 4)+
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("Hue") + xlab("Group")  +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12" , "Bright\nAge:12"))






rsidetheta

mr1.side.contr <- contrast(mr1.side.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr1.side.contr) ##output z CI

```

## Maxilla

```{r}
summary(mr1.maxi)
mr1.maxi.TypeAge <-lmer(h.theta_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.maxi)
mr1.maxi.EM <- emmeans(mr1.maxi.TypeAge, ~TypeAge)

plot.mr1.maxi <- plot(mr1.maxi.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.theta_s Maxilla", plotit = F)

head(plot.mr1.maxi)
plot.mr1.maxi$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr1.maxi$group <- c("BF", "DF", "DF" ,"BF")
plot.mr1.maxi$group1 <- c("A1", "A2", "A1" ,"A2")

rmaxitheta <- ggplot(plot.mr1.maxi, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  ggtitle("Maxilla") + 
  geom_hline(yintercept = plot.mr1.maxi[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") + 
  geom_point(size = 4)+
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("h.theta_s Maxilla") + xlab("Group")  +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12" , "Bright\nAge:12"))

rmaxitheta


mr1.maxi.contr <- contrast(mr1.maxi.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr1.maxi.contr) ##output z CI
```

## Mandible

```{r}
summary(mr1.mand)
mr1.mand.TypeAge <-lmer(h.theta_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.mand)
mr1.mand.EM <- emmeans(mr1.mand.TypeAge, ~TypeAge)

plot.mr1.mand <- plot(mr1.mand.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.theta_s mand", plotit = F)

head(plot.mr1.mand)
plot.mr1.mand$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr1.mand$group <- c("BF", "DF", "DF" ,"BF")
plot.mr1.mand$group1 <- c("A1", "A2", "A1" ,"A2")
rmandtheta <- ggplot(plot.mr1.mand, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  ggtitle("Mandible") + 
  geom_hline(yintercept = plot.mr1.mand[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") + 
  geom_point(size = 4)+
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("h.theta_s Mandible") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12")) + scale_y_continuous(
  labels = scales::number_format(accuracy = 0.1,
                                 decimal.mark = ','))

rmandtheta

mr1.mand.contr <- contrast(mr1.mand.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr1.mand.contr) ##output z CI
```

## Palate

```{r}
summary(mr1.pala)
mr1.pala.TypeAge <-lmer(h.theta_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.pala)
mr1.pala.EM <- emmeans(mr1.pala.TypeAge, ~TypeAge)

plot.mr1.pala <- plot(mr1.pala.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.theta_s pala", plotit = F)

head(plot.mr1.pala)
plot.mr1.pala$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr1.pala$group <- c("BF", "DF", "DF" ,"BF")
plot.mr1.pala$group1 <- c("A1", "A2", "A1" ,"A2")
rpalatheta <- ggplot(plot.mr1.pala, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  ggtitle("Palate") + 
  geom_hline(yintercept = plot.mr1.pala[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("h.theta_s Palate") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


rpalatheta

mr1.pala.contr <- contrast(mr1.pala.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(mr1.pala.contr) ##output z CI
```

# mr2 - h.phi

```{r}
#| echo: false
#| output: false
mr2.side <- lmer(h.phi_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.side)
mr2.maxi <- lmer(h.phi_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.maxi)
mr2.mand <- lmer(h.phi_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.mand)
mr2.pala <- lmer(h.phi_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.pala)

class(mr2.side) <- "lmerMod"
class(mr2.maxi) <- "lmerMod"
class(mr2.mand) <- "lmerMod"
class(mr2.pala) <- "lmerMod"
```

```{r}
#| echo: false
h.phi_s.sum <- stargazer(mr2.side, mr2.mand, mr2.maxi, mr2.pala, digits = 2, type = "text", style = "default", title = "h.phi_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))
```

## Side

```{r}
summary(mr2.side)
mr2.side.TypeAge <-lmer(h.phi_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.side)
mr2.side.EM <- emmeans(mr2.side.TypeAge, ~TypeAge)

plot.mr2.side <- plot(mr2.side.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.phi_s side", plotit = F)

head(plot.mr2.side)
plot.mr2.side$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr2.side$group <- c("BF", "DF", "DF" ,"BF")
plot.mr2.side$group1 <- c("A1", "A2", "A1" ,"A2")
rsidephi <- ggplot(plot.mr2.side, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr2.side[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("h.phi_s Side") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

rsidephi





mr2.side.contr <- contrast(mr2.side.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr2.side.contr) ##output z CI

```

## Maxilla

```{r}
summary(mr2.maxi)
mr2.maxi.TypeAge <-lmer(h.phi_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.maxi)
mr2.maxi.EM <- emmeans(mr2.maxi.TypeAge, ~TypeAge)


plot.mr2.maxi <- plot(mr2.maxi.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.phi_s Maxilla", plotit = F)

head(plot.mr2.maxi)
plot.mr2.maxi$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr2.maxi$group <- c("BF", "DF", "DF" ,"BF")
plot.mr2.maxi$group1 <- c("A1", "A2", "A1" ,"A2")
rmaxiphi <- ggplot(plot.mr2.maxi, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr2.maxi[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("h.phi_s Maxilla") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12")) + scale_y_continuous(
  labels = scales::number_format(accuracy = 0.1,
                                 decimal.mark = '.'))

rmaxiphi

mr2.maxi.contr <- contrast(mr2.maxi.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr2.maxi.contr) ##output z CI
```

## Mandible

```{r}
summary(mr2.mand)
mr2.mand.TypeAge <-lmer(h.phi_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.mand)
mr2.mand.EM <- emmeans(mr2.mand.TypeAge, ~TypeAge)
plot.mr2.mand <- plot(mr2.mand.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.phi_s mand", plotit = F)

head(plot.mr2.mand)
plot.mr2.mand$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr2.mand$group <- c("BF", "DF", "DF" ,"BF")
plot.mr2.mand$group1 <- c("A1", "A2", "A1" ,"A2")
rmandphi <- ggplot(plot.mr2.mand, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr2.mand[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("h.phi_s Mandible") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12")) + scale_y_continuous(
  labels = scales::number_format(accuracy = 0.1,
                                 decimal.mark = '.'))

rmandphi

mr2.mand.contr <- contrast(mr2.mand.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr2.mand.contr) ##output z CI
```

## Palate

```{r}
summary(mr2.pala)
mr2.pala.TypeAge <-lmer(h.phi_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.pala)
mr2.pala.EM <- emmeans(mr2.pala.TypeAge, ~TypeAge)

plot.mr2.pala <- plot(mr2.pala.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans h.phi_s pala", plotit = F)

head(plot.mr2.pala)
plot.mr2.pala$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr2.pala$group <- c("BF", "DF", "DF" ,"BF")
plot.mr2.pala$group1 <- c("A1", "A2", "A1" ,"A2")
rpalaphi <- ggplot(plot.mr2.pala, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr2.pala[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("h.phi_s Palate") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

rpalaphi

mr2.pala.contr <- contrast(mr2.pala.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(mr2.pala.contr) ##output z CI
```

# mr3 - r.achieved

```{r}
#| echo: false
#| output: false
mr3.side <- lmer( r.achieved_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.side)
mr3.maxi <- lmer( r.achieved_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.maxi)
mr3.mand <- lmer( r.achieved_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.mand)
mr3.pala <- lmer( r.achieved_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.pala)

class(mr3.side) <- "lmerMod"
class(mr3.maxi) <- "lmerMod"
class(mr3.mand) <- "lmerMod"
class(mr3.pala) <- "lmerMod"
```

```{r}
#| echo: false
 r.achieved_s.sum <- stargazer(mr3.side, mr3.mand, mr3.maxi, mr3.pala, digits = 2, type = "text", style = "default", title = " r.achieved_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))
```

## Side

```{r}
summary(mr3.side)
mr3.side.TypeAge <-lmer( r.achieved_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.side)
mr3.side.EM <- emmeans(mr3.side.TypeAge, ~TypeAge)


plot.mr3.side <- plot(mr3.side.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans  r.achieved_s Side", plotit = F)

head(plot.mr3.side)
plot.mr3.side$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr3.side$group <- c("BF", "DF", "DF" ,"BF")
plot.mr3.side$group1 <- c("A1", "A2", "A1" ,"A2")
rsideach <- ggplot(plot.mr3.side, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  scale_y_continuous(labels = number_format(accuracy = 0.1)) +
  geom_hline(yintercept = plot.mr3.side[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("r.achieved_s Side") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

rsideach

mr3.side.contr <- contrast(mr3.side.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr3.side.contr) ##output z CI

```

## Maxilla

```{r}
summary(mr3.maxi)
mr3.maxi.TypeAge <-lmer( r.achieved_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.maxi)
mr3.maxi.EM <- emmeans(mr3.maxi.TypeAge, ~TypeAge)


plot.mr3.maxi <- plot(mr3.maxi.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans  r.achieved_s Maxilla", plotit = F)

head(plot.mr3.maxi)
plot.mr3.maxi$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr3.maxi$group <- c("BF", "DF", "DF" ,"BF")
plot.mr3.maxi$group1 <- c("A1", "A2", "A1" ,"A2")
rmaxiach <- ggplot(plot.mr3.maxi, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr3.maxi[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("r.achieved_s Maxilla") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12")) + scale_y_continuous(  labels = scales::number_format(accuracy = 0.1,
                                  decimal.mark = ','))

rmaxiach

mr3.maxi.contr <- contrast(mr3.maxi.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr3.maxi.contr) ##output z CI
```

## Mandible

```{r}
summary(mr3.mand)
mr3.mand.TypeAge <-lmer( r.achieved_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.mand)
mr3.mand.EM <- emmeans(mr3.mand.TypeAge, ~TypeAge)


plot.mr3.mand <- plot(mr3.mand.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans  r.achieved_s Mandible", plotit = F)

head(plot.mr3.mand)
plot.mr3.mand$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr3.mand$group <- c("BF", "DF", "DF" ,"BF")
plot.mr3.mand$group1 <- c("A1", "A2", "A1" ,"A2")
rmandach <- ggplot(plot.mr3.mand, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr3.mand[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("r.achieved_s Mandible") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))
                                

rmandach

mr3.mand.contr <- contrast(mr3.mand.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr3.mand.contr) ##output z CI
```

## Palate

```{r}
summary(mr3.pala)
mr3.pala.TypeAge <-lmer( r.achieved_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.pala)
mr3.pala.EM <- emmeans(mr3.pala.TypeAge, ~TypeAge)


plot.mr3.pala <- plot(mr3.pala.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans  r.achieved_s pala", plotit = F)

head(plot.mr3.pala)
plot.mr3.pala$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr3.pala$group <- c("BF", "DF", "DF" ,"BF")
plot.mr3.pala$group1 <- c("A1", "A2", "A1" ,"A2")
rpalaach <- ggplot(plot.mr3.pala, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  scale_y_continuous(labels = number_format(accuracy = 0.1)) +
  geom_hline(yintercept = plot.mr3.pala[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("r.achieved_s Palate") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

rpalaach

mr3.pala.contr <- contrast(mr3.pala.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(mr3.pala.contr) ##output z CI
```

# mr4 - lum_s

```{r}
#| echo: false
#| output: false
mr4.side <- lmer(lum_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.side)
mr4.maxi <- lmer(lum_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.maxi)
mr4.mand <- lmer(lum_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.mand)
mr4.pala <- lmer(lum_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.pala)

class(mr4.side) <- "lmerMod"
class(mr4.maxi) <- "lmerMod"
class(mr4.mand) <- "lmerMod"
class(mr4.pala) <- "lmerMod"
```

```{r}
#| echo: false
lum_s.sum <- stargazer(mr4.side, mr4.mand, mr4.maxi, mr4.pala, digits = 2,  type = "text", style = "default", title = "lum_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))
```

## Side

```{r}
summary(mr4.side)
mr4.side.TypeAge <-lmer(lum_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.side)
mr4.side.EM <- emmeans(mr4.side.TypeAge, ~TypeAge)

plot.mr4.side <- plot(mr4.side.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans lum Side", plotit = F)

head(plot.mr4.side)

plot.mr4.side$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr4.side$group <- c("BF", "DF", "DF" ,"BF")


plot.mr4.side$group1 <- c("A1", "A2", "A1" ,"A2")
rsidelum <- ggplot(plot.mr4.side, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group)) +
  geom_hline(yintercept = plot.mr4.side[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) + theme(text = element_text(size = 12)) +
  theme_bw() + theme(legend.position = "none") +
  ylab("Luminance") + xlab("Group")
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))




mr4.side.contr <- contrast(mr4.side.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr4.side.contr) ##output z CI

```

## Maxilla

```{r}
summary(mr4.maxi)
mr4.maxi.TypeAge <-lmer(lum_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.maxi)
mr4.maxi.EM <- emmeans(mr4.maxi.TypeAge, ~TypeAge)

plot.mr4.maxi <- plot(mr4.maxi.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans lum Maxilla", plotit = F)

head(plot.mr4.maxi)

plot.mr4.maxi$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr4.maxi$group <- c("BF", "DF", "DF" ,"BF")
plot.mr4.maxi$group1 <- c("A1", "A2", "A1" ,"A2")

rmaxilum <- ggplot(plot.mr4.maxi, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr4.maxi[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) + theme(text = element_text(size = 12)) +
  theme_bw() + theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"), )


rsidelum <- ggplot(plot.mr4.side, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group)) +
  geom_hline(yintercept = plot.mr4.side[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) + theme(text = element_text(size = 12)) +
  theme_bw() + theme(legend.position = "none") +
  ylab("Luminance") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))





mr4.maxi.contr <- contrast(mr4.maxi.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr4.maxi.contr) ##output z CI
```

## Mandible

```{r}
summary(mr4.mand)
mr4.mand.TypeAge <-lmer(lum_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.mand)
mr4.mand.EM <- emmeans(mr4.mand.TypeAge, ~TypeAge)

plot.mr4.mand <- plot(mr4.mand.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans lum Mandible", plotit = F)

head(plot.mr4.mand)

plot.mr4.mand$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr4.mand$group <- c("BF", "DF", "DF" ,"BF")
plot.mr4.mand$group1 <- c("A1", "A2", "A1" ,"A2")
rmandlum <- ggplot(plot.mr4.mand, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr4.mand[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) + theme(text = element_text(size = 12)) +
  theme_bw() +theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("") + xlab("") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

mr4.mand.contr <- contrast(mr4.mand.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr4.mand.contr) ##output z CI
```

## Palate

```{r}
summary(mr4.pala)
mr4.pala.TypeAge <-lmer(lum_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.pala)
mr4.pala.EM <- emmeans(mr4.pala.TypeAge, ~TypeAge)

plot.mr4.pala <- plot(mr4.pala.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans lum Palate", plotit = F)

head(plot.mr4.pala)

plot.mr4.pala$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr4.pala$group <- c("BF", "DF", "DF" ,"BF")
plot.mr4.pala$group1 <- c("A1", "A2", "A1" ,"A2")
rpalalum <- ggplot(plot.mr4.pala, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr4.pala[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) + theme(text = element_text(size = 12)) +
  theme_bw() + theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))


mr4.pala.contr <- contrast(mr4.pala.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(mr4.pala.contr) ##output z CI
```

# mr5 - S9_s

```{r}
#| echo: false
#| output: false
mr5.side <- lmer(S9_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.side)
mr5.maxi <- lmer(S9_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.maxi)
mr5.mand <- lmer(S9_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.mand)
mr5.pala <- lmer(S9_s ~ Type * Age + (1|Individual) + (1|Nestbox), data = TCS_DB_data.pala)

class(mr5.side) <- "lmerMod"
class(mr5.maxi) <- "lmerMod"
class(mr5.mand) <- "lmerMod"
class(mr5.pala) <- "lmerMod"
```

```{r}
#| echo: false
S9_s.sum <- stargazer(mr5.side, mr5.mand, mr5.maxi, mr5.pala, type = "text", style = "default", title = "S9_s Mixed models (Estimate + (Std. Error)", column.labels = c("Side", "Maxilla", "Mandible", "Palate"))
```

## Side

```{r}
summary(mr5.side)
mr5.side.TypeAge <-lmer(S9_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.side)
mr5.side.EM <- emmeans(mr5.side.TypeAge, ~TypeAge)

plot.mr5.side <- plot(mr5.side.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans S9 Side", plotit = F)

head(plot.mr5.side)

plot.mr5.side$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr5.side$group <- c("BF", "DF", "DF" ,"BF")
plot.mr5.side$group1 <- c("A1", "A2", "A1" ,"A2")

rsideS9 <- ggplot(plot.mr5.side, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  scale_y_continuous(labels = number_format(accuracy = 0.1)) +
  geom_hline(yintercept = plot.mr5.side[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("S9 Side") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12")) + scale_y_continuous(labels = scales::number_format(accuracy = 0.1,
                             decimal.mark = ','))

mr5.side.contr <- contrast(mr5.side.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr5.side.contr) ##output z CI

```

## Maxilla

```{r}
summary(mr5.maxi)
mr5.maxi.TypeAge <-lmer(S9_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.maxi)
mr5.maxi.EM <- emmeans(mr5.maxi.TypeAge, ~TypeAge)

plot.mr5.maxi <- plot(mr5.maxi.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans S9 Maxilla", plotit = F)

head(plot.mr5.maxi)

plot.mr5.maxi$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr5.maxi$group <- c("BF", "DF", "DF" ,"BF")
plot.mr5.maxi$group1 <- c("A1", "A2", "A1" ,"A2")
rmaxiS9 <- ggplot(plot.mr5.maxi, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr5.maxi[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none", axis.title.y = element_blank()) +
  ylab ("S9 Maxilla") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

mr5.maxi.contr <- contrast(mr5.maxi.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr5.maxi.contr) ##output z CI
```

## Mandible

```{r}
summary(mr5.mand)
mr5.mand.TypeAge <-lmer(S9_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.mand)
mr5.mand.EM <- emmeans(mr5.mand.TypeAge, ~TypeAge)


plot.mr5.mand <- plot(mr5.mand.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans S9 Mandible", plotit = F)

head(plot.mr5.mand)

plot.mr5.mand$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr5.mand$group <- c("BF", "DF", "DF" ,"BF")
plot.mr5.mand$group1 <- c("A1", "A2", "A1" ,"A2")
rmandS9 <- ggplot(plot.mr5.mand, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr5.mand[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("S9 Mandible") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

mr5.mand.contr <- contrast(mr5.mand.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 

confint(mr5.mand.contr) ##output z CI
```

## Palate

```{r}
summary(mr5.pala)
mr5.pala.TypeAge <-lmer(S9_s ~ TypeAge + (1|Individual) + (1|Nestbox), data = TCS_DB_data.pala)
mr5.pala.EM <- emmeans(mr5.pala.TypeAge, ~TypeAge)

plot.mr5.pala <- plot(mr5.pala.EM, horizontal = FALSE, colors = "darkgreen", xlab = "emmeans S9 Palate", plotit = F)

head(plot.mr5.pala)

plot.mr5.pala$TypeAge <- c("Bright\nAge:8", "Bright\nAge:12", "Dark\nAge:8", "Dark\nAge:12")
plot.mr5.pala$group <- c("BF", "DF", "DF" ,"BF")
plot.mr5.pala$group1 <- c("A1", "A2", "A1" ,"A2")
rpalaS9 <- ggplot(plot.mr5.pala, aes(x = TypeAge, y = the.emmean, ymin =  lower.CL, ymax = upper.CL, color = group))  +
  geom_hline(yintercept = plot.mr5.pala[3, "the.emmean"], alpha = 0.5, lty = 2) +
  geom_line(aes(group = group1), color = "black") +
  geom_point(size = 4) +
  geom_errorbar(lwd = 1, width = 0) +
  theme_bw() + theme(text = element_text(size = 12)) +
  theme(legend.position = "none") +
  ylab ("S9 Palate") + xlab("Group") +
  scale_x_discrete(limits = c("Dark\nAge:8", "Bright\nAge:8", "Dark\nAge:12","Bright\nAge:12"))

mr5.pala.contr <- contrast(mr5.pala.EM, list(B1_D2 = c(-1,0,0,1), 
                                            D1_B2 = c(0,1,-1,0),
                                            B1_D1 = c(-1,0,1,0), 
                                            B2_D2 = c(0,1,0,-1))) 
confint(mr5.pala.contr) ##output z CI
```
