---
title: "Visual models"
author: "PP"
format: html
editor: visual
---

### **Set workspace and Libraries**

```{r}
#| context: setup
#| include: false

#set directory
knitr::opts_knit$set(root.dir = normalizePath("WORKING DIRECTORY PATH"))

#load libraries
 
```

### Open .RData file "data.RData"

`{load("../data.RData")}`

#data 'specs' consists of raw imported spectral data

Fix negative values to zero and average spectra by 2 subsequent measurements.

```{r}
specs <- procspec(specs, fixneg = 'zero')
meanspecs <- aggspec(specs, by = 2, FUN = mean) 
```

### Subseting data

Create labels for the time of the measurement "Age", and type of the nest box "BRIG" - bright, "DARK"

**Age** [- M1 or M2]{.underline} - represent the nestlings age M1 - 8 days old; M2 - 12 days old.\
**Exp** - [BF or DF]{.underline} - experimental group "Bright First" or "Dark First"\
**Type** - [BRIG or DARK]{.underline} - nest box type when the measurement was taken "BRIG" - bright or "DARK" - dark\
**Nestbox**- Three-digit number - nest box ID\
**ID** - Seven-digit code - Individual nestling ID, ring number\
**Region** - [P1, P2, P3, P4]{.underline} - beak's region P1 - Side, P2- Maxilla, P3 - Mandible, P4 - Palate

```{r}
Age <- (do.call(rbind, strsplit(names(meanspecs),"\\_"))[,1])
Exp  <- do.call(rbind, strsplit(names(meanspecs),"\\_"))[,2]
Type <- do.call(rbind, strsplit(names(meanspecs),"\\_"))[,3]
Nestbox <- do.call(rbind, strsplit(names(meanspecs),"\\_"))[,4]
ID <- do.call(rbind, strsplit(names(meanspecs),"\\_"))[,5]
Region <- do.call(rbind, strsplit(names(meanspecs),"\\_"))[,6]
```

Now subset each type of nest box to perform vismodels and smooth:

```{r}
dark.specs <- subset(meanspecs, subset = Type == "DARK")
dark.specs <- procspec(dark.specs, opt = "smooth", span = 0.2)

bright.specs <- subset(meanspecs, subset = Type == "BRIG")
bright.specs <- procspec(bright.specs, opt = "smooth", span = 0.2)

```

```{r}
#Subset for each beak region:
# Side <- subset(meanspecs, subset = Region == "P1")
# Maxilla <- subset(meanspecs, subset = Region == "P2")
# Mandible <- subset(meanspecs, subset = Region == "P3")
# Palate <- subset(meanspecs, subset = Region == "P4")
```

## Visual models

### Visual model for bright nest boxes

```{r}
is.rspec(bright.specs)
vm_bright <- vismodel(bright.specs, visual = "avg.uv", illum = bright.luminant, qcatch="Qi", relative=F, achromatic = "bt.dc", trans = "bluetit", vonkries = F)
```

### Visual model for dark nest boxes

```{r}
is.rspec(dark.specs) 
vm_dark <- vismodel(dark.specs, visual = "avg.uv", illum = dark.luminant, qcatch="Qi", relative=F, achromatic = "bt.dc", trans = "bluetit", vonkries = F) 
```

### Visual model for ideal illuminant

```{r}
is.rspec(meanspecs)
vm_ideal <- vismodel(meanspecs, visual = "avg.uv", illum = "ideal", qcatch="Qi", relative=F, achromatic = "bt.dc", trans = "bluetit", vonkries = F)

```

# **Noise-weighted Distances**

For Blue tit single cone ratio is 1, 1.92, 2.68, 2,70

Subset age groups from VM's

```{r}
#| output: false
vm_DarkA1 <- subset(vm_dark, "M1")
vm_DarkA2 <- subset(vm_dark, "M2")
vm_BrightA1 <- subset(vm_bright, "M1")
vm_BrightA2 <- subset(vm_bright, "M2")
vm_IdealA1<- subset(vm_ideal, "M1")
vm_IdealA2 <- subset(vm_ideal, "M2")
```

## Distances for dark nest boxes

### Age 8 days dark nest boxes:

```{r}
RegionsDarkA1 <- substr(rownames(vm_DarkA1), 24, 25)

bdist_DarkA1 <-bootcoldist(vm_DarkA1, by= RegionsDarkA1, n = c(1, 1.92, 2.68, 2.70), weber = 0.1, weber.achro = 0.1)

bdist_DarkA1



```

### Age 12 days dark nest boxes:

```{r}
RegionsDarkA2 <- substr(rownames(vm_DarkA2), 24, 25)

bdist_DarkA2 <-bootcoldist(vm_DarkA2, by= RegionsDarkA2, n = c(1, 1.92, 2.68, 2.70), weber = 0.1, weber.achro = 0.1)
bdist_DarkA2

```

### 8 + 12 days old dark nest boxes:

```{r}
RegionsDark <- substr(rownames(vm_dark), 24, 25)
bdist_Dark <-bootcoldist(vm_dark, by= RegionsDark, n = c(1, 1.92, 2.68, 2.70), weber = 0.1, weber.achro = 0.1)
bdist_Dark
```

### #PLOTS DARK

```{r}

#labels = c("Side-Maxilla", "Side-Mandible", "Side- Palate", "Maxilla - Mandible", "Maxilla - Palate", "Mandible - Palate"))

par(mfrow = c(3,2))

#DS A1
plot(bdist_DarkA1[,1],
     main = ("Dark 8 days old - Chromatic Contrast"),
     ylim = c(0, 8),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dS"
)
axis(1, at = 1:6, labels = rownames(bdist_DarkA1))
segments(1:6,bdist_DarkA1[,2],1:6, bdist_DarkA1[,3], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1

#DL A1
plot(bdist_DarkA1[,4],
     main = ("Dark 8 days old - Achromatic Contrast"),
     ylim = c(0, 8),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dL"
)
axis(1, at = 1:6, labels = rownames(bdist_DarkA1))
segments(1:6, bdist_DarkA1[,5], 1:6, bdist_DarkA1[,6], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1


#DS A2
plot(bdist_DarkA2[,1],
     main = ("Dark 12 days old - Chromatic Contrast"),
     ylim = c(0, 8),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dS"
)
axis(1, at = 1:6, rownames(bdist_DarkA2))
segments(1:6,bdist_DarkA2[,2],1:6, bdist_DarkA2[,3], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1


#DL A2
plot(bdist_DarkA2[,4],
     main = ("Dark 12 days old - Achromatic Contrast"),
     ylim = c(0, 8),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dL"
)
axis(1, at = 1:6, labels = rownames(bdist_DarkA2))
segments(1:6, bdist_DarkA2[,5], 1:6, bdist_DarkA2[,6], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1


#DS all ages
plot(bdist_Dark[,1],
     main = ("Dark - Chromatic Contrast"),
     ylim = c(0, 8),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dS"
)
axis(1, at = 1:6, labels = rownames(bdist_Dark))
segments(1:6,bdist_Dark[,2],1:6, bdist_Dark[,3], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1

#DL all ages
plot(bdist_Dark[,4],
     main = ("Dark - Achromatic Contrast"),
     ylim = c(0, 8),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dL"
)
axis(1, at = 1:6, labels = rownames(bdist_Dark))
segments(1:6,bdist_Dark[,5],1:6, bdist_Dark[,6], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1
```

### 

# Distances for bright nest boxes

```{r}
RegionsBrightA1 <- substr(rownames(vm_BrightA1), 24, 25)
bdist_BrightA1 <-bootcoldist(vm_BrightA1, by= RegionsBrightA1, n = c(1, 1.92, 2.68, 2.70), weber = 0.1, weber.achro = 0.1)
bdist_BrightA1

RegionsBrightA2 <- substr(rownames(vm_BrightA2), 24, 25)
bdist_BrightA2 <-bootcoldist(vm_BrightA2, by= RegionsBrightA2, n = c(1, 1.92, 2.68, 2.70), weber = 0.1, weber.achro = 0.1)
bdist_BrightA2

RegionsBright <- substr(rownames(vm_bright), 24, 25)
bdist_Bright <-bootcoldist(vm_bright, by= RegionsBright, n = c(1, 1.92, 2.68, 2.70), weber = 0.1, weber.achro = 0.1)
bdist_Bright
```

### #PLOTS BRIGHT

```{r}
par( mfrow = c(3,2))

#DS A1

plot(bdist_BrightA1[,1],
     main = "Bright 8 days old - Chromatic Contrast",
     ylim = c(0, 10),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dS"
)
axis(1, at = 1:6, labels = rownames(bdist_BrightA1))
segments(1:6,bdist_BrightA1[,2],1:6, bdist_BrightA1[,3], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1

#DL A1
plot(bdist_BrightA1[,4],
     main = "Bright 8 days old - Achromatic contrast",
     ylim = c(0, 10),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dL"
)
axis(1, at = 1:6, labels = rownames(bdist_BrightA1))
segments(1:6, bdist_BrightA1[,5], 1:6, bdist_BrightA1[,6], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1


# DS A2
plot(bdist_BrightA2[,1],
     main = "Bright 12 days old - Chromatic Contrast",
     ylim = c(0, 10),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dS"
)
axis(1, at = 1:6, labels = rownames(bdist_BrightA2))
segments(1:6,bdist_BrightA2[,2],1:6, bdist_BrightA2[,3], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1

#DL A2
plot(bdist_BrightA2[,4],
     main = "Bright 12 days old - Achromatic contrast",
     ylim = c(0, 10),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dL"
)
axis(1, at = 1:6, labels = rownames(bdist_BrightA2))
segments(1:6, bdist_BrightA2[,5], 1:6, bdist_BrightA2[,6], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1


#DS ALL
plot(bdist_Bright[,1],
     main = "Bright - Chromatic contrast",
     ylim = c(0, 10),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dS"
)
axis(1, at = 1:6, labels = rownames(bdist_Bright))
segments(1:6, bdist_Bright[,2],1:6, bdist_Bright[,3], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1
#DL ALL

plot(bdist_Bright[,4],
     main = "Bright - Achromatic contrast",
     ylim = c(0, 10),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "dL"
)
axis(1, at = 1:6, labels = rownames(bdist_Bright))
segments(1:6, bdist_Bright[,5],1:6, bdist_Bright[,6], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1
```

## Distances for ideal illuminant

### Age 8 days ideal illuminant:

```{r}
regionsidm1 <- substr(rownames(vm_ideal), 24, 25)
bdist_ideal_m1 <-bootcoldist(vm_ideal, by= regionsidm1, n = c(1, 1.92, 2.68, 2.70), weber = 0.1, weber.achro = 0.1)
bdist_ideal_m1

#DS
plot(bdist_ideal_m1[,1],
     ylim = c(0, 10),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "Chromatic contrast (dS)"
)
axis(1, at = 1:6, labels = rownames(bdist_ideal_m1))
segments(1:6,bdist_ideal_m1[,2],1:6, bdist_ideal_m1[,3], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1

#DL
plot(bdist_ideal_m1[,4],
     ylim = c(0, 10),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "Achromatic contrast (dL)"
)
axis(1, at = 1:6, labels = rownames(bdist_ideal_m1))
segments(1:6, bdist_ideal_m1[,5], 1:6, bdist_ideal_m1[,6], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1

```

### Age 12 days ideal illuminant:

```{r}
regionsidm2 <- substr(rownames(vm_ideal_m2), 24, 25)
bdist_ideal_m2 <-bootcoldist(vm_ideal_m2, by= regionsidm2, n = c(1, 1.92, 2.68, 2.70), weber = 0.1, weber.achro = 0.1)
bdist_ideal_m2

#DS
plot(bdist_ideal_m2[,1],
     ylim = c(0, 10),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "Chromatic contrast (dS)"
)
axis(1, at = 1:6, labels = rownames(bdist_ideal_m2))
segments(1:6,bdist_ideal_m2[,2],1:6, bdist_ideal_m2[,3], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1

#DL
plot(bdist_ideal_m2[,4],
     ylim = c(0, 10),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "Achromatic contrast (dL)"
)
axis(1, at = 1:6, labels = rownames(bdist_ideal_m2))
segments(1:6, bdist_ideal_m2[,5], 1:6, bdist_ideal_m2[,6], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1
```

### 8 +12 days old ideal illuminant:

```{r}
regionsid <- substr(rownames(vm_ideal), 24, 25)
bdist_ideal <-bootcoldist(vm_ideal, by = regionsid, n = c(1, 1.92, 2.68, 2.70), weber = 0.1, weber.achro = 0.1)
bdist_ideal

#DS
plot(bdist_ideal[,1],
     ylim = c(0, 8),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "Chromatic contrast (dS)"
)
axis(1, at = 1:6, labels = rownames(bdist_ideal))
segments(1:6, bdist_ideal[,2],1:6, bdist_ideal[,3], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1

#DL
plot(bdist_ideal[,4],
     ylim = c(0, 8),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "Achromatic contrast (dL)"
)
axis(1, at = 1:6, labels = rownames(bdist_ideal))
segments(1:6, bdist_ideal[,5],1:6, bdist_ideal[,6], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1
```

### 8 +12 days old standard illuminant by experimental groups:

```{r}
regionsid <- substr(rownames(vm_ideal), 24, 25)
bdist_ideal <-bootcoldist(vm_ideal, by = regionsid, n = c(1, 1.92, 2.68, 2.70), weber = 0.1, weber.achro = 0.1)
bdist_ideal

#DS
plot(bdist_ideal[,1],
     ylim = c(0, 8),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "Chromatic contrast (dS)"
)
axis(1, at = 1:6, labels = rownames(bdist_ideal))
segments(1:6, bdist_ideal[,2],1:6, bdist_ideal[,3], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1

#DL
plot(bdist_ideal[,4],
     ylim = c(0, 8),
     pch = 10,
     bg = 1,
     cex = 2,
     xaxt = "n",
     xlab = "Centroid comparison",
     ylab = "Achromatic contrast (dL)"
)
axis(1, at = 1:6, labels = rownames(bdist_ideal))
segments(1:6, bdist_ideal[,5],1:6, bdist_ideal[,6], lwd = 2) # Add CI's
abline(h = 1, lty = 3, lwd = 2) # Add a 'threshold' line at dS = 1
```
